Proposed Solution

### 2016-11-11 Ennan-Proposal/prelim.tex
stuff

From ConfigC we drew the main inspiration for this proposal. We now briefly
outline how does ConfigC work. It first automatically
analyzes a dataset of correct configuration files to derive
 rules for describing a specification. Before that process even starts,
we identified several basic types, 
such Boolean, Integer, File. With each of these types we associated a 
list of templates. We then analyze the given training data set of 
correct configuration files and derive rules describing variable                                                                                                                                                                                                                                                                                                                                                                                                                       
relations. We illustrate how is this done on two fragments of 
configuration files given in Fig.~\ref{fig:twoFiles}.  When analyzing
a file, we first assign a type to every 
keyword. After that we instantiate each type-associated template with 
the concrete keywords and we save the learned set 
of rules. For instance, with the integer type we only associated comparison templates ($X < Y, X = Y, \ldots$). After 
analyzing File\_1, the set of learned rules will contain the following rules:
\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
max_connections=300
mysql.max_persistent=200
max_connections > mysql.max_persistent
\end{lstlisting}
The set of learned rules is changing with every file that we analyze: contradicting 
files are removed and new rules are added. In practice, this process is done 
in parallel.

After analyzing File$_2$ the rule \texttt{max\_connections = 300} is removed.

@@

Once this preprocessing of training data is done, the resulting language model, 
together with accompanying rules, 
is used to detect errors in new configuration files given by the user.

Additional to the described process we also developed algorithms for the 
misconfigurations that cannot easily be templated. All together, ConfigC 
can detect the following errors:
missing entries, ordering errors, type errors and
simple value correlations. Running ConfigC on Example~1 from 
Sec.~\ref{sec:intro-examples} returns the following output:
\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
ORDERING ERROR: Expected extension "recode.so" BEFORE 
extension "mysql.so"
\end{lstlisting} 
ConfigC could not detect an error present in Example~2 since it can detect 
only simple comparison-based relations.

To our knowledge, there is no existing effort that is able to detect
the above errors, because they are very tricky to identify in
practice.

@@

\paragraph{Evaluations on ConfigC.}
We implemented a prototype system by following 
our ConfigC design~\cite{santolucitoCAV}.
In order to demonstrate the capability of ConfigC,
we evaluated the ConfigC prototype based on real-world
MySQL configuration files~\cite{configdataset} 
containing tricky misconfiguration errors,
such as entry missing errors, ordering errors, and
value correlation errors.
We extracted 20 MySQL configuration files to detect, 
and grouped them into four categories according to their
error types: missing entry, type error, ordering error
and value correlation.
Table~\ref{table:res} shows the evaluation results we use
ConfigC to detect configuration errors in these 20 real-world
configuration files.
As shown in Table~\ref{table:res},
ConfigC is able to successfully report the misconfiguration problems.

@@

\paragraph{Limitations.}
ConfigC still has the following limitations.

@@

\item ConfigC requires the datasets of configuration files for training 
  have to be correct, which is hard to achieve in practice, since 
  it is difficult for administrators or users to offer a
  set of 100\% correct configuration files for training.

>>>>

From ConfigC we drew the main inspiration for this proposal. We now briefly
outline how does ConfigC work. It first automatically
analyzes a dataset of correct configuration files to derive
 rules for describing a specification. Before that process even starts,
we identified several basic types, 
such Boolean, Integer, File. With each of these types we associated a 
list of templates. We then analyze the given training data set of 
correct configuration files and derive rules describing variable                                                                                                                                                                                                                                                                                                                                                                                                                       
relations. We illustrate how is this done on two fragments of 
configuration files given in Fig.~\ref{fig:twoFiles}.  When analyzing
a file, we first assign a type to every 
keyword. After that we instantiate each type-annotated template with 
concrete keywords and we save the learned set 
of rules. For instance, with the integer type we only associated comparison templates ($X < Y, X = Y, \ldots$). After 
analyzing File\_1, the set of learned rules will contain the following rules:
\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
max_connections=300
mysql.max_persistent=200
max_connections > mysql.max_persistent
\end{lstlisting}
The set of learned rules is changing with every file that we analyze: contradicting 
files are removed and new rules are added. After analyzing File\_2 the rule \texttt{max\_connections = 300} is removed. In practice, this process is done 
in parallel.

@@

Additionally to the described process, we also developed algorithms for 
the misconfigurations that cannot easily be templated. All together, 
ConfigC can detect the following errors:
missing entries, ordering errors, type errors and
simple value correlations. Once this preprocessing of training data is 
done, the resulting language model, 
together with accompanying rules, 
is used to detect errors in new configuration files given by the user.

Running ConfigC on Example~1 from 
Sec.~\ref{sec:intro-examples} returns the following output:
\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
ORDERING ERROR: Expected extension "recode.so" BEFORE 
extension "mysql.so"
\end{lstlisting} 
ConfigC could not detect an error present in Example~2 since it can detect 
only simple comparison-based relations.

\iffalse

@@

\fi

@@

We implemented a prototype and evaluated it on 
real-world MySQL configuration files~\cite{configdataset}.
We manually extracted 20 files that contained errors which our tool 
can detect and grouped them into four categories according to their
error types: missing entry, type error, ordering error
and value correlation. The evaluation results are shown in 
Table~\ref{table:res}. We can see that the our tool can detect most of 
the errors, with a low number of false positives. We believe that further
studies in this direction will bring us better results

\subsection{Limitations of ConfigC}
Despite promising early results, ConfigC was a first experimental attempt 
into formal verification of configuration files, and as such it still has several limitations.

@@

\item ConfigC works on the premise that training dataset consists only 
of correct files, which is hard to achieve in practice. In the 
prototype we manually checked every file in the prototype. Clearly, this approach will not scale and  since 
  it is difficult for administrators or users to offer a
  set of 100\% correct configuration files for training.
